\chapter*{Acknowledgements}

I want to thank everyone who has helped me with this thesis work. It was a great learning experience for me.\\
\\
First of all, I would like to thank Peter Verschut, the project manager at SPC, who has made this project possible. By providing the SPC lab at MIC and letting me do experiments with the machines, I could get a lot of practical experience with the Fanuc210F and other machines. Also he connected me with experts in the field so I could make contacts for further work in the field of robotics. \\
\\
Dimitri Jeltsema gave me a good hint how to model and control the robot based on the content of his lectures. Besides that, Ellen Wesselingh and Trung Nguyen have given me great advice on the writing and modelling of the robot. Without your guidance this journey would have been a lot harder. Your critical questioning and pushing in the right direction have helped me a lot. Thank you for your patience and effort. \\
\\
Peter Corke has made the modelling and control of the robot arm a lot easier for me with the toolbox that he distributes for free. I hope, this toolbox will see many more iterations with additional functionalities and improvements.\\
\\
Aliya Patel, a fellow master student working on another type of robot was a great help in the practical part of the project. Also besides the work, I am happy to have you as a friend. I wish you success in your career and I hope you will get to work in your field of interest.\\
\\
Also Didier, Suzanne, Ivan and the other employees and students at SPC were always there, when I needed a helping hand. We were a great team.\\
\\
I would also like to thank Bram and his colleagues from Qing for the great collaboration.\\
\\
Special thanks goes to Karlijn who has kept me sane in times of isolation due to Covid-19. Thanks for the moral support!\\
\\
Finally, I would like to thank my Mother and her partner Gerhard for making this master studies possible for me.
